Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2018-09-14 paper/drafts/draft_final.tex

\documentclass[conference]{IEEEtran}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Paper Title*\\
	{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
		should not be used}
	\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Adithya Ravishankara}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	\and
	\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	\and
	\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	}
	\section{1}
	\subsection{Intro to mav and control system architecture}
	Multirotor Aerial Vehicles (MAV), specifically quadrotors, have become quite commonplace in many industries ranging from filmography to racing to even military operations. Over the past decade, there has been an incredible amount of research and advancement within this field leading to its proliferation and allowing for the technology to become more accessible. One of the major areas of research regarding MAV's is the control system that directs the motor-rotor system. The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables. The control of the motor-rotor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propeller, all the way to the high level control system of the ESC. \\
	In general, there are two different types of control loops; open and closed. Open control loops are what the majority of MAV control systems are. There is a flight controller, that sends a signal to the ESC that applies a particular voltage to the motor based on previously calibrated settings. In this method, the final result of the motor spinning is unknown to the flight controller. Therefore given any disturbances, there will be large variances in the response of the overall system. In response to these systems there are smarter, closed loop control. This is the type of control we will focus on. Closed loop systems provide a certain way to measure the output of the rotor based on the input from the FC. This allows for a smarter, more robust system and greater control of the output. \\
	\subsection{Intro to the problem}
	The main problem we are trying to answer is how to create an effective, efficient, and reasonable solution to having a closed loop control system. This would include having a type of sensor which would measure the thrust output of the propellor and relay that onto the ESC so that the ESC can control the thrust output accordingly.
	\subsection{Lit review}
		Mahoney et al (2017) have developed an algorithm which bases the control system around an estimation of the thrust from a propeller based on the voltage and current given to the motor by the ESC. Their system works to maintain a thrust given some disturbance. From looking over their algorithm, they have a system which runs through a for loop before detecting an appropriate response to extraneous forces. This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible. As well this method of thrust based control requires a significant amount of calibration for both the propellers and

@@

	\subsection{1.4}
	The scope of this paper is to introduce a wind sensor as an external sensor and develop the relationship between the downwash rotor wind speed and the thrust vector of the propeller. Doing that we can implement a control system by which the wind sensor can be used to maintain a thrust given disturbances or faults within the system. 

@@

	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say 

@@

	\subsection{Experimental Setup- How we set up the kalman/Algorithm}
	\begin{figure}[]
		\includegraphics[width=\textwidth]{block_diagram}
		\caption{Block Diagram}
		\label{block_diagram}
	\end{figure}

	We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value. The first, main value, is from the wind sensor which is measured through an Arduino. The voltage value that the arduino measures is then converted to a thrust value through the power function
	\begin{equation}
	Thrust = 4.701 * 10^{15} * V_w^{6.146} + 0.0731
	\label{wind_power}
	\end{equation}

	The second measurement of thrust is a polynomial function that converts the recorded PWM value that is used to control the propeller to thrust. \newline
	\begin{eqnarray}
	Thrust = 1.957*10^{-5}*PWM^4 \\
	- 7.476*10^{-4}*PWM^3 \nonumber\\ 
	+ 1.272*10^{-2}*PWM^2 \nonumber\\
	+ .01092*PWM - .01842 \nonumber
	\label{pwm_poly}
	\end{eqnarray}

@@

	\subsection{The tests}
	To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response. The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust. To do this we measured  As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely. This result gives us the confidence to setup the PI based on the kalman filter's value.

	To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system. The first step was to create an external disturbance by placing another propeller and blowing wind perpendicular to the axis of the main propeller. This would be akin to horizontal crosswind flow across the propeller.
	\begin{figure}
		\label{content...}
	\end{figure}
	 Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through
	\begin{figure}
		content...
	\end{figure}
	Next we 
	\subsection{4.3}
	\subsection{4.4}

@@

	\subsection{Reiteration of results}
	In this paper we introduced a hot wire anemometer with the function of measuring the downwash rotor wind speed on MAV's. By this measurement we can calculate the thrust output of the propeller and 
	\subsection{Reiteration of applications}
	\subsection{Shortcomings and limitations}
	\subsection{5.4}

	\begin{thebibliography}{99}
		\bibitem{Mahoney1} Mahoney 2012
		\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
		\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
		\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Paper Title*\\
	{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
		should not be used}
	\thanks{Identify applicable funding agency here. If none, delete this.}
}
\author{\IEEEauthorblockN{1\textsuperscript{st} Adithya Ravishankara}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	\and
	\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	\and
	\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	}
	\section{Intro}
	\subsection{Intro to mav and control system architecture}
	Multirotor Aerial Vehicles (MAV), specifically quadrotors, have become quite commonplace in many industries ranging from filmography to racing to even military operations. Over the past decade, there has been an incredible amount of research and advancement within this field leading to its proliferation and allowing for the technology to become more accessible. One of the major areas of research regarding MAV's is the control system that directs the motor-rotor system. The control mechanism ranges in complexity from the common motor-rotor control, to a more complex system that takes into consideration parameters such as thrust or torque. The control of the motor-rotor has to account for multiple different external and internal factors, from the ambient wind speed, the rotation speed of the propeller (RPM), the pitch of the propeller, and for more complex controllers, the internal loops of the Electronic Speed Controller (ESC) or Flight Controller (FC). \\
	In general, there are two different types of control loops; open and closed. Open control loops are what the majority of MAV control systems are. There is an FC, that sends a value to the ESC that applies a particular voltage to the motor based on previously calibrated settings. In this method, the final result of the motor spinning is unknown to the flight controller. Therefore given any disturbances, there will be large variances in the response of the overall system. In response to these systems there are smarter, closed loop control. This is the type of control we will focus on. Closed loop systems provide a certain way to measure the output of the rotor based on the input from the FC. This allows for a smarter, more robust system and greater control of the output. \\
	\subsection{Intro to the problem}
	The problem we address with this paper is on how to create an effective, efficient and reasonable closed loop control system for MAV motor-rotors. This would require a method to measure the thrust output of the MAV, relay the information back to the system upon which the system would correct for any errors due to disturbances.
	\subsection{Lit review}
	Mahoney et al (2017) have developed an algorithm which bases the control system around an estimation of the thrust from a propeller based on the voltage and current given to the motor by the ESC. Their system works to maintain a thrust given some disturbance. From looking over their algorithm, they have a system which runs through a for loop before detecting an appropriate response to extraneous forces. This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible. As well this method of thrust based control requires a significant amount of calibration for both the propellers and 

@@

	\subsection{Scope and application}
	The scope of this paper is to introduce a wind sensor as an external sensor and develop the relationship between the downwash rotor wind speed and the thrust vector of the propeller. Doing that we can implement a closed loop control system by which the wind sensor can be used to maintain a thrust given disturbances or faults within the system. This allows for the MAV to have a more accurate and reliable response but also allows for a more agile system. In this sense for applications such as drone racing, filmography, and even research, it would allow for a smoother and and more stable system. 

@@

	Since we are doing only the static tests in this paper, we can disregard the horizontal components of the wind as well as the body frame velocities. Then we can state 

@@

	\subsection{Experimental Setup- How we set up the kalman/Algorithm}
	\begin{figure}[]
		\includegraphics[width=\textwidth]{block_diagram}
		\caption{Block Diagram}
		\label{block_diagram}
	\end{figure}
	We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value. The first, main value, is from the wind sensor which is measured through an Arduino. The voltage value that the arduino measures is then converted to a thrust value through the power function
	Thrust = 4.701 * 10^{15} * V_w^{6.146} + 0.0731
	\label{wind_power}
	The second measurement of thrust is a polynomial function that converts the recorded PWM value that is used to control the propeller to thrust. \newline
	Thrust = 1.957*10^{-5}*PWM^4 \\
	- 7.476*10^{-4}*PWM^3 \nonumber\\ 
	+ 1.272*10^{-2}*PWM^2 \nonumber\\
	+ .01092*PWM - .01842 \nonumber
	\label{pwm_poly}

@@

	\subsection{The tests}
	To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response. The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust. To do this we measured  As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely. This result gives us the confidence to setup the PI based on the kalman filter's value. 
	To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system. The first step was to create an external disturbance by placing another propeller and blowing wind perpendicular to the axis of the main propeller. This would be akin to horizontal crosswind flow across the propeller.
	\begin{figure}
		\label{content...}
	\end{figure}
	 Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through
	\begin{figure}
		content...
	\end{figure}
	Next we 
	\subsection{4.3}
	\subsection{Shortcomings and limitations}
	low wind speed. Have not accounted for multiple sources of wind. fixed and controlled environment. only one propeller. 

@@

	\subsection{Reiteration of results}
	In this paper we presented a closed loop control system for the purposes of controlling MAV rotor systems by the introduction of a hot wire anemometer. The anemometer measures the rate of wind flow from the downwash of the MAV rotor and there is a linear relationship that is developed between wind flow velocity and the thrust output of the system. Through this relationship we developed a PI controller that corrects for any errors in thrust output due to both internal and external disturbances.
	\subsection{Reiteration of applications}

	\subsection
	\subsection{5.4}
	\begin{thebibliography}{99}
		\bibitem{Mahoney1} Mahoney 2012
		\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
		\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
		\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471

### 2018-09-14 paper/drafts/litrev.tex

\$ Control systems on multirotor aerial vehicles have had many different iterations, each of which have added a significant level of control to the system. The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables. The control of a multirotor propellor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propellor, all the way to the high level control system of the ESC. \\

>>>>

Control systems on multirotor aerial vehicles have had many different iterations, each of which have added a significant level of control to the system. The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables. The control of a multirotor propellor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propellor, all the way to the high level control system of the ESC. \\
